The corona of a fully convective star with a near-polar flare

### 2023-10-03 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}
TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=$\LXLbol in quiescence is about an order of magnitude lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime of partly and fully convective M dwarfs~\citep{wright2011stellaractivityrotation,wright2018stellar}. In the Hyades and Praesepe, \citet{nunez2022factory} cover both fully convective and rapidly rotating M dwarfs, and find a downward trend in $L_X/L_{\rm bol}$ with decreasing rotation period for M3.5-M7 dwarfs. This tentatively points toward a supersaturation of the corona at fast rotation speeds, as has been suggested before for M~dwarfs~\citep{jeffries2011investigating}, but also earlier type stars~\citep{prosser1996rosat, argiroffi2016supersaturation} and even red giants~\citep{dixon2020rotationally}. However, none of the aforementioned M~dwarf studies probe below spectral type M6.

>>>>

\subsection{X-ray luminosity}
\label{sec:discussion:xraylum}

\begin{figure}
    \script{FIGURE_LXLBol_rot.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/lx_lbol.png}
        \caption{$L_X/L_{\rm bol}$ over rotation period of stars of different spectral types. For partially convective dwarfs, and fully convective mid-M dwarfs, we show the results from~\citet{wright2011stellaractivityrotation, wright2016solartype}, color-coded by $V-K$ magnitude. Late M dwarfs from the literature are marked with diamonds, and are detailed in Table~\ref{tab:latmlxlbol}. TIC~277 is shown as red star. The few late M dwarfs with known rotation period and X-ray luminosity show a tentative decline in $L_X/L_{\rm bol}$ relative to earlier fully convective dwarfs, which might be due to polar updraft migration~(see Section \ref{sec:discussion:xraylum}).
        }
        \label{fig:lx_lbol}
    \end{centering}
\end{figure}

TIC~277's coronal luminosity relative to bolometric luminosity of $L_X/L_{\rm bol}=$\LXLbol in quiescence is about an order of magnitude lower than the $L_X/L_{\rm bol}\sim 10^{-3}$ average in the saturated regime of partly and fully convective M dwarfs~\citep[Fig.~\ref{fig:lx_lbol},][]{wright2011stellaractivityrotation,wright2016solartype}. In the Hyades and Praesepe, \citet{nunez2022factory} cover both fully convective and rapidly rotating M dwarfs, and find a downward trend in $L_X/L_{\rm bol}$ with decreasing rotation period for M3.5-M7 dwarfs. This tentatively points toward a supersaturation of the corona at fast rotation speeds, as has been suggested before for M~dwarfs~\citep{jeffries2011investigating}, but also earlier type stars~\citep{prosser1996rosat, argiroffi2016supersaturation} and even red giants~\citep{dixon2020rotationally}. However, none of the aforementioned M~dwarf studies probe below spectral type M6.
